\disstitle

### 2018-06-15 dissertation.tex
add mcmc chapters
camera geometry
further improvement
change abstract

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{import}
\usepackage{xspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{memhfixc}
\usepackage{miscstyle}

\newcommand{\disstitle}{Geometric Information for Image Understanding}

@@

\abstract
{
  \SingleSpacing
    Deep neural networks as one of the machine learning categories have been proposed
    since 1980s and proved successful in recent years. This thesis proposes methods which
    leverage deep neural networks to solve the camera geo-calibration problem, which is
    one of the import computer vision tasks. Furthermore, we also use the geo-calibration
    information (geo-location, orientation, etc.) to boost the training of the deep neural
    networks for image understanding.
    Our work focuses on three primary research areas: 1) estimating vanishing points
    and horizon line using image global context computed with deep neural networks. 2)
    domain adaptation from the ground image semantics to the satellite image semantics,
    and 3) learning transient feature representations for webcam images using the time
    and geo-location information in a semi-supervised manner.
    The primary contribution of this thesis is to explore the relation between the
    camera calibration information and image semantics, and bridge the gap between
    two research domains using deep neural networks, which provides us new ways for
    camera calibration and network training.
}
\keywords{ deep neural networks, computer vision, geo-calibration}

@@

\inject{introduction}
%\inject{background}
%\inject{dependence}
%\inject{discussion}

>>>>

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{import}
\usepackage{xspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{memhfixc}
\usepackage{algorithm2e, algorithmic}
\usepackage{soul}
\usepackage{miscstyle}

\newcommand{\disstitle}{Camera Geometry Detection and Use for Image
Understanding}

@@

\abstract
{
  \SingleSpacing
  Camera geometry is one of the fundamental elements in computer vision.
  It plays an essential role in many applications like depth estimation
  and image mensuration. 
  %
  In recent years, the rise of deep neural networks (DNNs) had changed
  the game in many computer vision areas, their ability of abstracting
  high-level semantic knowledges makes a lot of hard challenges
  solvable. 
  %
  This thesis mainly explores the possibility of combining camera
  geometry and DNNs. That is 1) Detecting camera geometry using DNNs,
  and 2) Training DNNs with camera geometric information.  Our work
  includes two research targets: The first part of this thesis focuses
  on camera geometry detection with DNNs, and the rest of it
  demonstrates how camera geometry can boost the learning of DNNs.
  %
  The primary contribution of this thesis is to explore the relation
  between camera geometry and image semantics, and bridge the gap
  between these two research domains, which provides us new ways for
  both camera calibration and deep neural network training.
}
\keywords{ camera geometry, deep neural networks, computer vision}

@@

\inject{introduction}
%\inject{mcmc}
%\inject{background}
%\inject{discussion}
